# Data Quality Metrics
First, I import the packages that I use in this section and read in the uncleaned data.

## Libararies

The libraries loaded in below acts as a list of all of the libraries that will be used in this document. 

```{r, message=FALSE, warning=FALSE}

###############################################
##########    ###  LIBRARIES  ###    ##########
###############################################

library(tidyverse)
library(plotly)
library(ggplot2)
library(gganimate)
library(magick)
library(gifski)
library(png)
library(knitr)
library(PerformanceAnalytics)
library(ggpubr)
library(lubridate)
library(ggthemes)
library(extrafont)
library(tm)
library(tidytext)
library(textdata)
library(gridExtra)
library(scales)
library(wordcloud)
library(reshape2)
library(textstem)
library(RColorBrewer)
library(echarts4r)
library(devtools)
library(rayshader)
library(kableExtra)
library(stringi)

```

```{r}

# SETTING UP FORMATTING 

kableFormat <- function(dat, caption) {
  kable(dat, "html", escape = FALSE, caption = caption) %>%
  kable_styling(bootstrap_options = c("striped", "condensed", "bordered"),
                full_width = FALSE)
}

```

## The Functions

## Quality Assessments
We assessed data quality using the metrics outlined in Pipino, Lee, and Wang (2002). For each of these metrics, we provide a brief commentary on how the data fared. Several of the data quality metrics were more pertinent to our analysis, so we provide deeper insight into them.